Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2023-12-01 article.qmd
Change phrasing regading solver tolerance

To test the reproducibility of results of SimBio,
we considered the first 100 curated models from BioModels.
As SimBio does not yet support the full SBML standard,
for instance, events,
we simulated only 60 of those.
Using the results from COPASI as ground truth,
SimBio reproduces the results within the solver tolerances.

>>>>

To test the reproducibility of results of SimBio,
we considered the first 100 curated models from BioModels.
As SimBio does not yet support the full SBML standard (for instance, events),
we could only simulate 60 of those.
Using the results from COPASI as ground truth,
SimBio reproduces the results with numerical differences depending on the solver tolerance.
